\tool: Revisiting BadUSB with Type-C

### 2021-01-28 WOOT/BadUSBC.tex

\begin{abstract}
The security of USB protocol has been paid extensive attention to, despite its wide usage.
Due to the \textit{trust-by-default} characteristics, USB security has caused serious problems.
For example, a well-known firmware attack, BadUSB, performs malicious operations on the victim hosts through disguising normal USB devices as human interface devices like keyboards and mice.
However, BadUSB suffers from several limitations.
Attackers cannot obtain the status of user interface to conduct precise attacks, and they may be detected by multiple effective countermeasures.
In this work, we extended BadUSB to support the new features of USB Type-C and proposed a multi-mode attack model, \tool.
It can obtain UI status to make attacks more precise and effective, and also bypass existing defense methods for BadUSB.
To our best knowledge, \tool is the first attack model utilizing USB Type-C.
To validate the usability and effectiveness, we conducted extensive experiments and a user study, in which 
\fengwei{What results?}we got valuable results.
\fengwei{what countermeasures do we propose? including isolated UI rendering.}
We also proposed reasonable countermeasures for our attack model, which may be inspiring for future research on defense methods.
\end{abstract}

>>>>

\begin{abstract}
The security of USB protocol has been paid extensive attention to, despite its wide usage.
Due to the \textit{trust-by-default} characteristics, USB security has caused serious problems.
For example, a well-known firmware attack, BadUSB, performs malicious operations on the victim hosts through disguising normal USB devices as human interface devices like keyboards and mice.
However, BadUSB suffers from several limitations.
Attackers cannot obtain the status of user interface to conduct precise attacks, and they may be detected by multiple effective countermeasures.
In this work, we extended BadUSB to support the new features of USB Type-C and proposed a multi-mode attack model, \tool.
It can obtain UI status to make attacks more precise and effective, and also bypass existing defense methods for BadUSB.
To our best knowledge, \tool is the first attack model utilizing USB Type-C.
To validate the usability and effectiveness, we conducted extensive experiments and a user study, in which 
\fengwei{What results?}we got valuable results.
\fengwei{what countermeasures do we propose? including isolated UI rendering.}
We also proposed reasonable countermeasures for our attack model, including isolated UI rendering, external hardware authorization and distrust-by-default, which may be inspiring for future research on defense methods.
\end{abstract}

### 2021-01-28 WOOT/Files/badusb.tex

The advantage of this mode is that it archives defense bypass and attack
feedback with low overhead.  \fengwei{I don't understand the sentence below.}
As mentioned above, we only require video stream at the beginning (defense
bypass) and the end (result feedback) of the attack. Moreover, with mouse
supported, \tool extends the original BadUSB attack surface and perform well in
mobile device.

\textbf{Privacy Extraction Mode.} \tool under this mode does not emulate other
USB device and solely relies on the video stream function of USB 3.x; it uses
``Video Capture'' component to transmit the stream to the embedded
computer\fengwei{What is embedded computer? Do we define this in the previous
text?}. The victim's device would mistakenly treat \tool as an external monitor
and output its video stream. This stream is latter processed by the embedded
computer to extract private data.

>>>>

The advantage of this mode is that it archives defense bypass and attack
feedback with video streaming.  \fengwei{I don't understand the sentence below.}\hongyi{Fixed, I think it's redundant and less important}
%As mentioned above, we only require video stream at the beginning (defense
%bypass) and the end (result feedback) of the attack. 
Moreover, with mouse
supported, \tool extends the original BadUSB attack surface and perform well in
mobile device.

\textbf{Privacy Extraction Mode.} \tool under this mode does not emulate other
USB device and solely relies on the video stream function of USB 3.x; it uses
``Video Capture'' component to transmit the stream to embedded ``Single Board Computer''\fengwei{What is embedded computer? Do we define this in the previous\hongyi{Fixed by using the term mentioned in Figure}
text?}. The victim's device would mistakenly treat \tool as an external monitor
and output its video stream. This stream is latter processed by the embedded
computer to extract private data.

### 2021-01-28 WOOT/Files/related_work.tex

From the hardware perspective, the BadUSB attack requires `D-' and `D+' pins which
are defined by the protocol to transmitting data. Without these pins, data cannot 
be transferred via USB cable. Based
on this fact, USB Condom \cite{Condom} is a hardware solution to block data
channels by adding a blocker in the connector. This blocker can cut off the `D-'
and `D+' connection while leaving power pins intact.  However, this method poses
a great challenge to the plug-and-play property of USB, as once it is deployed, it
stops all USB functions other than charging.

Under the premise of ensuring the full functionality of USB devices, some works
try to improve the security during connection establishment.  Windows Defender
ATP~\cite{windenfenderwhite} maintains a whitelist of USB devices, only devices
on the whitelist are allowed to communicate with the host. This prevents all
potential attacks from untrusted devices. But this requires users to have a
certain safety awareness and technical background to maintain a valid
whitelist. For example, a naive user may add the USB device from unknown
sources to his/her whitelist without precaution. Some designs can overcome
this drawback. For instance, Mohammadmoradi et
al.\cite{mohammadmoradi2018making} propose a strategy to generate such a
whitelist automatically. This strategy first generates a unique fingerprint for
each device based on its functionality. Then these fingerprints are used to
maintain a safe and valid whitelist of USB devices. There is another work
mediating USB connectivity for Industrial Control. TMSUI~\cite{yang2015tmsui}
relies on the rich experience of administrators to build a whitelist. However, some
modified USB devices may hide their real functionality from the user.

To solve this flaw, GoodUSB~\cite{tian2015defending} will\fengwei{Don't use future tense. We can just use resent tense.} report the functionality claimed by the device to the user and let the user decides whether to authorize. When a device is plugged in, GoodUSB will load its driver but limit its functionality until a series of authorizations are completed. These authorizations are designed to be performed manually. As BadUSB is normally unable to obtain the video stream of the host, an attacker cannot complete this authorization with an automatic script. Thus this defense is sufficient for a normal BadUSB attack. But if the attacker has the access to victim's screen, GoodUSB will be bypassed easily as the attacker can just complete this authorization manually and perform subsequent attacks.

After the USB enumeration and driver loading, there are\fengwei{I feel too many "there are" style sentences.} also works trying to archive `defense in depth' against BadUSB attack.  Neuner et al.~\cite{neuner2018usblock}\fengwei{Typicall, we add "~" to create a space for each citation.} prevents BadUSB attacks from the malicious flash drive by analyzing the temporal characteristics of BadUSB-like attacks. This defense mechanism is effective because the attacker cannot obtain the screen of the host using BadUSB. In this case, the malicious device can only inject key stoke in a very short time to reduce the risk of being discovered. This defect causes the typing characteristics of BadUSB to be detectable. Pham et al.~\cite{pham2010optimizing} optimizing windows security features. It can block the execution of unsigned files, the installation of unsigned drivers carried on portable media. Moreover, in GoodUSB, a VM is deployed in the host to as a honeypot to detect and stop malicious behavior of USB devices.

In addition to injection attacks, data theft attack is also one of the focuses of the academic community. As mentioned in Section~\ref{subsec:usb_attack}, there exists an attack called JFC (juicy film charging)\cite{JFC} which abuses the MHL standard to steal video stream from the victim. In order to mitigate this issue, Meng et al.\cite{meng2018252} proposed a statistical model using status like GPU/CPU usage to detect JFC attack.

>>>>

From the hardware perspective, the BadUSB attack requires `D-' and `D+' pins which
are defined by the protocol to transmitting data. Without these pins, data cannot 
be transferred via USB cable. Based
on this fact, USB Condom~\cite{Condom} is a hardware solution to block data
channels by adding a blocker in the connector. This blocker can cut off the `D-'
and `D+' connection while leaving power pins intact. However, this method poses
a great challenge to the plug-and-play property of USB, as once it is deployed, it
stops all USB functions other than charging.

Under the premise of ensuring the full functionality of USB devices, some works
try to improve the security during connection establishment.  Windows Defender
ATP~\cite{windenfenderwhite} maintains a whitelist of USB devices, only devices
on the whitelist are allowed to communicate with the host. This prevents all
potential attacks from untrusted devices. But this requires users to have a
certain safety awareness and technical background to maintain a valid
whitelist. For example, a naive user may add the USB device from unknown
sources to his/her whitelist without precaution. Some designs can overcome
this drawback. For instance, Mohammadmoradi et
al.~\cite{mohammadmoradi2018making} propose a strategy to generate such a
whitelist automatically. This strategy first generates a unique fingerprint for
each device based on its functionality. Then these fingerprints are used to
maintain a safe and valid whitelist of USB devices. There is another work
mediating USB connectivity for Industrial Control. TMSUI~\cite{yang2015tmsui}
relies on the rich experience of administrators to build a whitelist. However, some
modified USB devices may hide their real functionality from the user.

To solve this flaw, GoodUSB~\cite{tian2015defending} reports the functionality claimed
by the device to the user and let the user decides whether to authorize. When a device
is plugged in, GoodUSB will load its driver but limit its functionality until a
series of authorizations are completed. These authorizations are designed to be
performed manually. As BadUSB is normally unable to obtain the video stream of
the host, an attacker cannot complete this authorization with
an automatic script. Thus this defense is sufficient for normal BadUSB attack. But
if the attacker has the access to victim's screen, GoodUSB will be bypassed
easily as the attacker can just complete this authorization manually and
perform subsequent attacks.

After the USB enumeration and driver loading, there are
also works trying to archive `defense in depth'
against BadUSB attack.  Neuner et 
al.~\cite{neuner2018usblock}
prevents BadUSB attacks from the malicious flash drive by analyzing
the temporal characteristics of BadUSB-like attacks. This defense mechanism is
effective because the attacker cannot obtain the screen of the host using
BadUSB. In this case, the malicious device can only inject key stoke in a very
short time to reduce the risk of being discovered. This defect causes the
typing characteristics of BadUSB to be detectable. Pham et
al.~\cite{pham2010optimizing} optimize windows security features. It can
block the execution of unsigned files and the installation of unsigned drivers
carried on portable media. Moreover, in GoodUSB, a VM is deployed in the host to as
a honeypot to detect and stop malicious behavior of USB devices.

In addition to injection attacks, data theft attack is also one of the focuses
of the academic community. As mentioned in Section~\ref{subsec:usb_attack}, there
exists an attack called JFC (juicy film charging)~\cite{JFC} which abuses the MHL
standard to steal video stream from the victim. In order to mitigate this
issue, Meng et al.~\cite{meng2018252} proposed a statistical model using status
like GPU/CPU usage to detect JFC attack.
